\Large Clustering Vehicle Trips Identified from Automatic \\ Number Plate Recognition Camera Scans

### 2018-02-01 trips.tex
Fixed maths formula in duplicate scannings subsection
Finished text on errors scans

\begin{equation} \label{e.sighting.different}
t^{k}_{i} \ne t^{k}_{j} \Rightarrow s^{k}_{i} \ne s^{k}_{j} \ , \ i \ne j
\end{equation}

@@

Even though number plate recognition cameras have accuracy rates of 99.9\% or higher, on average 1 observation out of 1000 is a misclassified plate number. We categorise the errors made by ANPR cameras into two types:
\begin{enumerate}
  \item a passing vehicle is not detected by the camera;
  \item a different vehicle is detected instead.
\end{enumerate}
In the first case, there is no observed data. The corresponding trip sequence for the affected vehicle will be missing a sighting but we will have no indication of this. On the second case, there is a recorded sighting, but this will be assigned to the incorrect vehicle.

>>>>

\begin{align} \label{e.sighting.different.2}
 (\ c^{k}_{i} &\ne c^{k}_{j} \, )\ \vee \\
 (\ c^{k}_{i} &= c^{k}_{j} \wedge |t^{k}_{i} - t^{k}_{j}| < \gamma \, )\ \Rightarrow s^{k}_{i} \ne s^{k}_{j}  \ , \ i \ne j \nonumber
\end{align}

@@

Number plate recognition cameras have accuracy rates of 99.9\% or higher. If we consider that on average 1 to 10 out of 10000 scans are misclassified plate number then approximately 200 to 2000 scans everyday are incorrect scans. We categorise the errors made by ANPR cameras into two types:
\begin{enumerate}
  \item a passing vehicle is not detected by the camera;
  \item a different vehicle is detected instead.
\end{enumerate}
In the first case, there is no observed data. The corresponding trip sequence for the affected vehicle will be missing a sighting but we will have no indication of this. On the second case, there is a recorded sighting, but this will be assigned to the incorrect vehicle. Even though, the camera provides a value of \emph{confidence} which helps in diagnosing incorrect scans, errors still occur for high values of confidence. Even though that in this work we do not present a complex solution for this issue, methods to detect and address these two types of errors need to be designed and implemented in the future.
